Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Reformatted the GLAD/EDGI, NBR and RAMP employment graph

dat.retro %>% 
  ggplot(aes(x = employment_prior_covid, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Employment distribution of the retro cohorts",
       x = "",
       y = "") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

>>>>

dat.retro_employment_plot <- dat.retro %>% 
  group_by(Sample_plot, employment_prior_covid) %>% 
  summarise(n = n()) %>% 
  drop_na()

dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000))
